---
title: "Reproducing Lambert et al."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reproducing Lambert et al.}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignetter allows for a guide to reproducing all results from Lambert et al.
This document functions as a makefile to allow for step-by-step directions to
running all models.

Disclaimer: None of the code shown in this vignette is run. This is due to the 
computational demands of the analysis. All analyses from the paper were run
using the Peregrine High Performance Cluster Computer at the University of 
Groningen. 

```{r setup}
library(relaxedDAISIE)
```


## Empirical Analysis

Individuals archipelagos can be analysed by calling the respective
*_model.sh file, for example:

```{bash eval=FALSE}
Aldabra_Group_models.sh
```

All archipelago model can be run in parallel by running:

```{bash eval=FALSE}
run_all_archipelago_models.sh
```

Once the models have been run the best maximum likelihood model can be extracted
from the replicates using:

```{r eval=FALSE}

find_max_loglik(archipelago = "Aldabra_Group")
``` 

